Structural replication of nanoporous media using procedural noise

### 2018-05-29 ms.tex
Updated gofr and refs

The field of synthetic rocks is a large field both scientifically and technologically \cite{biswal2007stochastic,hamzehpour2006development,Reconstructing random media}. 
Methods to generate synthentic rock samples from experimental characterizations may be based on purely statistical or geometrical models, models of physical processes that generate the samples, or combinations of both. 
For small-scale porous media, physical models are often used to generate initial grain packings \cite{pilotti1998generation,scott1969density,herrmann2013physics}, then further mechano-chemical and fluid-mediated processes such as precipitation-dissoluton processes and pressure solution \cite{rutter1983pressure}, or fracture and plastic deformation processes are added to include effects of long-term compaction \cite{rutter1983pressure,renard1997pressure}. 
On large scales, reservoir models are populated by statistical models for lithological and geomorphological processes \cite{pyrcz2014geostatistical}, such as river fan formation to generate particular grain size distributions \cite{koltermann1996heterogeneity,blair1994alluvial}. 
More statistical approaches include variations of percolation models \cite{sahimi} or network models \cite{fatt1956network,sahimi1993flow} to characterize and generate uncorrelated or correlated porous media. 
In addition, the high resolution of observational methods allow three-dimensional scans to form the basis for atomic-scale modeling using molecular modeling methods such as molecular dynamics or Monte Carlo methods to study the dynamics of nanoporous media. 
But then procedural or physical models are needed to fill in the atomic scale details, to build many statistical realizations of nanoporous media with atomic-scale details, and to extrapolate to larger scale models.

@@

\begin{figure}
\includegraphics[width=.45\textwidth]{gofr_plot.png}
\caption{$g(r)$ for three data sets: the simulated SiO$_2$ input data set (red), the best-fit parameter model (blue) and a random low-fit parameter model (green). \todo{Bytt denne figuren med VMD sin beregning. Normaliseringen vår er gal.}}
\label{fig:gofr1}
\end{figure}
Finally, we depict a comparison of the actual simulated input SiO$_2$ data set together with a representation of the best-fit parameters in figure \ref{fig:porous_vs_model}   
\begin{figure}
\includegraphics[width=.45\textwidth]{comparison.png}
\caption{Right side: A realisation of the best-fit parameters $\tau=-0.2$, $\psi=0.8$ and $\nu=0.3$. Left side: Simulated SiO$_2$ input data set used for parameter estimation. Although the pore geometry seems to be similar, we see some artifacts, such as single loose atoms in the generated geometry.}
\label{fig:porous_vs_model}
\end{figure}

@@

%\begin{thebibliography}{9}

%\bibitem[Groeneboom2014]{groeneboom2014} Groeneboom, N.~E., \& Dahle, H.\ 2014, \apj, 783, 138

%\end{thebibliography}

>>>>

The field of synthetic rocks is a large field both scientifically and technologically \citep{biswal2007stochastic,hamzehpour2006development, yeong1998reconstructing}. 
Methods to generate synthentic rock samples from experimental characterizations may be based on purely statistical or geometrical models, models of physical processes that generate the samples, or combinations of both. 
For small-scale porous media, physical models are often used to generate initial grain packings \cite{pilotti1998generation,scott1969density,herrmann2013physics}, then further mechano-chemical and fluid-mediated processes such as precipitation-dissoluton processes and pressure solution \cite{rutter1983pressure}, or fracture and plastic deformation processes are added to include effects of long-term compaction \cite{rutter1983pressure,renard1997pressure}. 
On large scales, reservoir models are populated by statistical models for lithological and geomorphological processes \cite{pyrcz2014geostatistical}, such as river fan formation to generate particular grain size distributions \cite{koltermann1996heterogeneity,blair1994alluvial}. 
More statistical approaches include variations of percolation models \cite{sahimi} or network models \cite{fatt1956network,sahimi1993flow} to characterize and generate uncorrelated or correlated porous media. 
In addition, the high resolution of observational methods allow three-dimensional scans to form the basis for atomic-scale modeling using molecular modeling methods such as molecular dynamics or Monte Carlo methods to study the dynamics of nanoporous media. 
But then procedural or physical models are needed to fill in the atomic scale details, to build many statistical realizations of nanoporous media with atomic-scale details, and to extrapolate to larger scale models.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{gofr_figure.pdf}
\caption{$g(r)$ for three data sets: the simulated SiO$_2$ input data set (red), the best-fit parameter model (blue) and a random low-fit parameter model (green).}
\label{fig:gofr1}
\end{figure}
Finally, we depict a comparison of the actual simulated input SiO$_2$ data set together with a representation of the best-fit parameters in figure \ref{fig:porous_vs_model}   
\begin{figure}
\includegraphics[width=.45\textwidth]{comparison.png}
\caption{Right side: A realisation of the best-fit parameters $\tau=-0.2$, $\psi=0.8$ and $\nu=0.3$. Left side: Simulated SiO$_2$ input data set used for parameter estimation. Although the pore geometry seems to be similar, we see some artifacts, such as single loose atoms in the generated geometry.}
\label{fig:porous_vs_model}
\end{figure}

@@
